Milestone 2: Core results 01

### 2023-03-22 R_codeP01/reports/MS2_report02.Rmd
PCA in report

>>>>

# START USING DOMAIN KNOWLEDGE

# PCA on signature gene sets, cross-validation
### Ridge: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_pca_c_771_RORprolif.RData")
r_pca_c_771_RORprolif <- report02_out_ridge(r_pca_c_771_RORprolif)
```

### Ridge: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_pca_c_interact_771_RORprolif.RData")
r_pca_c_interact_771_RORprolif <- report02_out_ridge(r_pca_c_interact_771_RORprolif)
```

### Lasso: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_771_RORprolif.RData")
l_pca_c_771_RORprolif <- report02_out(l_pca_c_771_RORprolif)
```

### Lasso: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/l_pca_c_interact_771_RORprolif.RData")
l_pca_c_interact_771_RORprolif <- report02_out(l_pca_c_interact_771_RORprolif)
```

### ElasticNet: 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_771_RORprolif.RData")
en_pca_c_771_RORprolif <- report02_out(en_pca_c_771_RORprolif)
```

### ElasticNet: 771 genes -> ROR-proliferation score + interactions between PCs
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/en_pca_c_interact_771_RORprolif.RData")
en_pca_c_interact_771_RORprolif <- report02_out(en_pca_c_interact_771_RORprolif)
```

LAGE TABELLER HER
